Manuscript plots

### 2023-11-15 manuscript_modelling_and_plots.Rmd
new code for saving figures at dpi of 300 for AAP spec + n-back performance data

```{r}
# load n-back data
n_back_performance <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Vehicle data/Processed data/n_back/n_back_performance.csv"))

@@

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/n_back_age_performance.tiff"), plot = n_back_age_performance , width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

# saving final plot
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/posterior.mu.tiff"), plot = sge.plot, width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

# saving plots
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/posterior.sigma.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

# plot saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/posterior.mean.intervals.sge.n.tiff"), plot = posterior.mean.intervals.sge, width = 16, height = 10, units = 'cm', dpi = 600, type = 'cairo')
```

@@

# data saving
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/proportion_pop_2_back.tiff"), plot = population.plot, width = 16, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/posterior.mu.gte.tiff"), plot = gte.plot, width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/posterior.sigma.gte.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

# posterior conditional means for n-back/no n-back and posterior predictive intervals
posterior.mean.intervals.gte <- entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  ggplot(aes(x = gte.norm, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = means, .width = c(.50, .95), position = position_nudge(y = -0.3)) +
  stat_interval(aes(x = .prediction), data = preds, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47), height = .03, alpha = .2) +
  scale_y_discrete(labels = c('No N-back','N-back')) +
  scale_color_brewer("Posterior predictive interval") +
  xlab(expression("Predicted" ~ italic(H[t]))) +
  ylab("Secondary task") +
  scale_x_continuous(breaks = seq(0, .2, .05)) +
  facet_wrap(~ lead, labeller = labeller(lead = l.labs),  ncol = 1) +
  #theme_plot +
  theme(legend.position = c(.5, .95), legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/posterior.mean.intervals.gte.n.tiff"), plot = posterior.mean.intervals.gte, width = 16, height = 10, units = 'cm', dpi = 600, type = 'cairo')
```

@@

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/proportion_pop_2_back_gte.tiff"), plot = population.plot.gte, width = 16, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/proportion_pop_2_back_gte_sigma.tiff"), plot = population.plot.sigma.gte, width = 16, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/fixation_state_space .tiff"), plot = age.nback.effect.sge , width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

@@

ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/age.nback.effect.tiff"), plot = age.nback.effect.gte, width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

>>>>

```{r}
# load n-back data
n_back_performance <- fread(file = here::here("gaze_entropy_heterogenous/data/n_back_performance.csv"))

@@

# plot saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig5.tiff"), plot = n_back_age_performance , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# saving final plot
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig6.tiff"), plot = sge.plot, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# saving plots
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig7.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# plot saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig8.tiff"), plot = posterior.mean.intervals.sge, width = 16, height = 10, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# data saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig9.tiff"), plot = population.plot, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig10.tiff"), plot = gte.plot, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig11.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# posterior conditional means for n-back/no n-back and posterior predictive intervals
posterior.mean.intervals.gte <- entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  ggplot(aes(x = gte.norm, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = means, .width = c(.50, .95), position = position_nudge(y = -0.3)) +
  stat_interval(aes(x = .prediction), data = preds, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47), height = .03, alpha = .2) +
  scale_y_discrete(labels = c('No N-back','N-back')) +
  scale_color_brewer("Posterior predictive interval") +
  xlab(expression("Predicted" ~ italic(H[t]))) +
  ylab("Secondary task") +
  scale_x_continuous(breaks = seq(0, .2, .05)) +
  facet_wrap(~ lead, labeller = labeller(lead = l.labs),  ncol = 1) +
  theme_plot +
  theme(legend.position = c(.5, .95), legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig12.tiff"), plot = posterior.mean.intervals.gte, width = 16, height = 10, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig13.tiff"), plot = population.plot.gte, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig14.tiff"), plot = population.plot.sigma.gte, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig15.tiff"), plot = age.nback.effect.sge , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig16.tiff"), plot = age.nback.effect.gte, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```
